---
title: "WM_selection"
author: "Nieto_Lopez"
date: "8/29/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Loading packages  
```{r}
library(tidyverse)
library(ggplot2)

```
Reading data  
```{r}
WM <- read.csv("data/WM-2015-2016-2017_fixingproductnames.csv", stringsAsFactors = TRUE)# Making the columns as factors
  WM$Year <- as.factor(WM$Year)# Changing the level of year to factor
  WM$Collection_ID <- as.numeric(WM$Collection_ID)# The goal is to change  the level of Collection to numeric, but for some reason, it should be by step by step. Changing the level of year to numeric in first approach 
  WM$Collection_ID <- as.character(WM$Collection_ID)#Changing the level of year to character as second approach
  levels(WM$Origin )[levels(WM$Origin ) == "trial"] <- "Fungicide field trials"#Changing the name to be more specific
  levels(WM$Origin )[levels(WM$Origin ) == "Survey"] <- "Farmer fields"#Changing the name to be more specific
  levels(WM$DNA.Extraction )[levels(WM$DNA.Extraction ) == ""] <- "No DNA extraction"#Changing the name to be more specific
  levels(WM$DNA.Extraction )[levels(WM$DNA.Extraction ) == "No"] <- "No DNA extraction"#Changing the name to be more specific
  levels(WM$DNA.Extraction )[levels(WM$DNA.Extraction ) == "Yes"] <- "Yes DNA extraction"#Changing the names to be more specific
usa <- map_data("usa")# USA map 
states <- map_data("state")# USA map by states
counties <- map_data("county")# USA map by counties
bra <- map_data("worldHires", "Brazil")
mexico <- map_data("worldHires", "Mexico")

mid_west_county <-
  subset(
    counties,
    region == "nebraska" |
      region == "wisconsin" | region == "michigan" | region == "iowa"
  )

```
Setting some objects previuosly work with
```{r}
tested <-
  c(
    "1",
    "118",
    "123",
    "12B",
    "129",
    "20",
    "21",
    "449",
    "461",
    "467",
    "475",
    "558",
    "564",
    "568",
    "581",
    "645",
    "800",
    "667",
    "74SS1",
    "8",
    "87",
    "318",
    "413",
    "419",
    "62-02",
    "62-03",
    "62-04",
    "78-01",
    "78-02",
    "78-05",
    "H-01",
    "H-03",
    "H-04",
    "I-20",
    "S-01",
    "W212",
    "1025",
    "1026",
    "1027",
    "1029",
    "1032",
    "1033",
    "1870",
    "1872",
    "1884",
    "1885",
    "54C",
    "65B",
    "51C",
    "71B",
    "64D",
    "53B",
    "60A",
    "698",
    "699",
    "710",
    "711",
    "724",
    "725",
    "731",
    "732",
    "738",
    "739",
    "746",
    "751",
    "755",
    "756",
    "757",
    "764",
    "765",
    "771",
    "772",
    "786",
    "787",
    "811",
    "812",
    "813",
    "814",
    "817",
    "818",
    "851",
    "852",
    "853",
    "855",
    "858",
    "859",
    "860",
    "861",
    "862",
    "867",
    "870",
    "871",
    "877",
    "878",
    "884",
    "885",
    "891",
    "892",
    "896",
    "897",
    "901",
    "902",
    "905",
    "906",
    "908",
    "909",
    "911",
    "912",
    "914",
    "274",
    "307",
    "504",
    "505",
    "2384",
    "2385",
    "2386",
    "2388",
    "2407",
    "2408",
    "2383",
    "1058",
    "1081",
    "1087",
    "1109",
    "1127",
    "1128",
    "1134",
    "1135",
    "1139",
    "1175",
    "1026",
    "1027",
    "1029",
    "1328",
    "1329",
    "1330",
    "1331",
    "1332",
    "1340",
    "1345",
    "1365",
    "1366",
    "1392",
    "1327",
    "1502",
    "1582",
    "1620",
    "1622",
    "1541",
    "1671",
    "1672",
    "1691",
    "1692",
    "1712",
    "1713",
    "1721",
    "1722",
    "1731",
    "1732",
    "1791",
    "1",
    "118",
    "123",
    "20",
    "74SS1",
    "8",
    "419",
    "78-02",
    "H-01",
    "H-03"
  )#Fungicide pre-tested isolates from USA midwestand including baselines  
mexican_isolates <- c("1857":"1940")#Fungicide pre-tested isolates from Mexico
```

White Mold selection from USA midwest  
Data wrangling
```{r}
  wm1 <-
  WM %>% select(
    Collection_ID,
    State,
    Field,
    Year,
    Origin,
    long,
    lat,
    hyphal_tip..ht.,
    DNA.Extraction,
    County,
    Serial_agar_dilution_for_creating_the_model_..N.20.,
    Form.ID
  )# Selecting 15 the most important columns so far

wm1_ <-  wm1 %>%
  mutate(Fungicide_status = ifelse(Collection_ID  %in% tested,
                                   "tested", "no_tested")) %>%# Creating a new column based wheather or not funcides pretested
  filter(!Collection_ID %in% mexican_isolates) %>%#Taking out mexican isolates
  group_by(Field) %>% mutate (num_isolates_per_field = ifelse(n() > 2, "2>isolates/Field", "<2isolates/Field")) %>%#Creating a new column if the number of isolates/field is major than 2
  ungroup()

wm1_$num_isolates_per_field <- as.factor(wm1_$num_isolates_per_field)#Converting as factor the levels of the new columns

```
Cleaning and making some arrangemments from the inventory so far, run twice
```{r}
wm1_ <- wm1_[-970, ]# Taking out this column that is in blank
wm1_$long <- as.numeric(as.character(wm1_$long))# Transforming long variables to numeric
wm1_$long <- (wm1_$long) * -1 # Transforming the long variable to the Hemispher West side

```
Subsetting some data
```{r}
# Creating the base map for subsequent plots
mid_west_base <-
  ggplot(data = mid_west_county,
         mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "grey")
# Creating the Master Dataframe about selection
selection <-
  wm1_ %>% select(# selecting the most important 15 columns plus the new one created
    Collection_ID,
    State,
    County,
    Field,
    Year,
    Origin,
    long,
    lat,
    hyphal_tip..ht.,
    DNA.Extraction,
    Serial_agar_dilution_for_creating_the_model_..N.20.,
    Form.ID,
    Fungicide_status,
    num_isolates_per_field
  ) %>% 
  arrange(factor (State, levels = c("NE", "IA", "WI", "MI"))) %>%#Arrange in this order from left to right in the US map  
  group_by(State, County, Field) %>%# grouping in order to select those with >=3 isolates/field/County/State 
  mutate(num_ISO_per_field = n()) %>%# Creating the column to count them 
  ungroup %>%
  group_by(State, County) %>%# grouping in order to select those   fields(>=3 isolates)/County/State 
  mutate(num_field_County = length(unique(factor(Field)))) %>%# Creating the column to count them 
  select(# Ordering the collumns to easy visulalization
    Collection_ID,
    State,
    County,
    Field,
    num_ISO_per_field,
    num_field_County,
    Year,
    Origin,
    long,
    lat,
    hyphal_tip..ht.,
    DNA.Extraction,
    Serial_agar_dilution_for_creating_the_model_..N.20.,
    Form.ID,
    Fungicide_status,
    num_isolates_per_field
  )
#Subdata for randomly selection of those 3 isolates/field/county/state 
selection1 <- selection %>%
  ungroup() %>%
  group_by(State, County, Field) %>%#grouping in order to select 3 isolates/field/County/State 
  filter(num_ISO_per_field > 10,
         Fungicide_status == "no_tested") %>%# Filtering those fields with more than 10 isolates/ field and also by no fungicide pre-tested. Here the original idea was to filter by 3 >= isolates but  it does not not work with the next pipe available from tidyverse 
  sample_n(3, replace = F) #Randomly sampled 3 isolates from the 10 available from each group 

# Subdata another one to work with those groups with less than 10 isolates and more or equal to 3 isolates. The way to do it was to rest to the ones done 
selection2 <- selection %>%# using the master dataframe
  ungroup() %>%
  group_by(State, County, Field) %>%#grouping in order to select 3 isolates/field/County/State 
  filter(!num_ISO_per_field %in% selection1$num_ISO_per_field) %>%
  filter(Fungicide_status == "no_tested") %>%#filterring those already done and also by no fungicide pre-tested
  ungroup()

```
Finding randomly either by function or by hand writing  3 samples for each (by sample function) field for those groupings with less than 10 isolates/field. In those cases of error it is due there is less than 3 isolates per field but it still being okay 

```{r}
fields1 <- selection2 %>%
  filter(State == "NE", County == "Valley", Field == "va")
a <- sample(fields1$Collection_ID, size = 3, replace = FALSE)# sampling 3 for each group

fields2 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "ant")
b <- sample(fields2$Collection_ID, size = 3, replace = FALSE)

fields3 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "21")
c <- sample(fields3$Collection_ID, size = 3, replace = FALSE)

fields4 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "22")
d <- sample(fields4$Collection_ID, size = 3, replace = FALSE)

fields5 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "23")
e <- sample(fields5$Collection_ID, size = 3, replace = FALSE)

fields6 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "24")
f <- sample(fields6$Collection_ID, size = 3, replace = FALSE)

fields7 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "25")
g <- sample(fields7$Collection_ID, size = 3, replace = FALSE)

fields8 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "69")
h <- sample(fields8$Collection_ID, size = 3, replace = FALSE)

fields9 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "75")
i <- sample(fields9$Collection_ID, size = 3, replace = FALSE)

fields10 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "102")
#j <- sample(fields10$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields11 <- selection2 %>%
  filter(State == "NE", County == "Antelope", Field == "103")
#k <- sample(fields11$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields12 <- selection2 %>%
  filter(State == "NE", County == "Cedar", Field == "6")
l <- sample(fields12$Collection_ID, size = 3, replace = FALSE)

fields13 <- selection2 %>%
  filter(State == "NE", County == "Cedar", Field == "67")
m <- sample(fields13$Collection_ID, size = 3, replace = FALSE)

fields14 <- selection2 %>%
  filter(State == "NE", County == "Cedar", Field == "78")
n <- sample(fields14$Collection_ID, size = 3, replace = FALSE)

fields15 <- selection2 %>%
  filter(State == "NE", County == "Cedar", Field == "98")
o <- sample(fields15$Collection_ID, size = 3, replace = FALSE)

fields16 <- selection2 %>%
  filter(State == "NE", County == "Cedar", Field == "100")
p <- sample(fields16$Collection_ID, size = 3, replace = FALSE)

fields17 <- selection2 %>%
  filter(State == "NE", County == "Cedar", Field == "101")
q <- sample(fields17$Collection_ID, size = 3, replace = FALSE)

fields18 <- selection2 %>%
  filter(State == "NE", County == "Greeley", Field == "8")
r <- sample(fields18$Collection_ID, size = 3, replace = FALSE)

fields19 <- selection2 %>%
  filter(State == "NE", County == "Greeley", Field == "9")
s <- sample(fields19$Collection_ID, size = 3, replace = FALSE)

fields20 <- selection2 %>%
  filter(State == "NE", County == "Greeley", Field == "68")
#t <- sample(fields20$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields21 <- selection2 %>%
  filter(State == "NE", County == "Madison", Field == "10")
u <- sample(fields21$Collection_ID, size = 3, replace = FALSE)

fields22 <- selection2 %>%
  filter(State == "NE", County == "Madison", Field == "11")
v <- sample(fields22$Collection_ID, size = 3, replace = FALSE)

fields23 <- selection2 %>%
  filter(State == "NE", County == "Boone", Field == "18")
w <- sample(fields23$Collection_ID, size = 3, replace = FALSE)

fields24 <- selection2 %>%
  filter(State == "NE", County == "Boone", Field == "19")
x <- sample(fields24$Collection_ID, size = 3, replace = FALSE)

fields25 <- selection2 %>%
  filter(State == "NE", County == "Boone", Field == "20")
y <- sample(fields25$Collection_ID, size = 3, replace = FALSE)

fields26 <- selection2 %>%
  filter(State == "NE", County == "Boone", Field == "45")
z <- sample(fields26$Collection_ID, size = 3, replace = FALSE)

fields27 <- selection2 %>%
  filter(State == "NE", County == "Boone", Field == "46")
aa <- sample(fields27$Collection_ID, size = 3, replace = FALSE)

fields28 <- selection2 %>%
  filter(State == "NE", County == "Boone", Field == "48")
bb <- sample(fields28$Collection_ID, size = 3, replace = FALSE)

fields29 <- selection2 %>%
  filter(State == "NE", County == "Dodge", Field == "34")
cc <- sample(fields29$Collection_ID, size = 3, replace = FALSE)

fields30 <- selection2 %>%
  filter(State == "NE", County == "Dodge", Field == "35")
dd <- sample(fields30$Collection_ID, size = 3, replace = FALSE)

fields31 <- selection2 %>%
  filter(State == "NE", County == "Holt", Field == "47")
ee <- sample(fields31$Collection_ID, size = 3, replace = FALSE)

fields32 <- selection2 %>%
  filter(State == "NE", County == "Sherman", Field == "60")
ff <- sample(fields32$Collection_ID, size = 3, replace = FALSE)

fields33 <- selection2 %>%
  filter(State == "NE", County == "Kearney", Field == "62")
gg <- sample(fields33$Collection_ID, size = 3, replace = FALSE)

fields34 <- selection2 %>%
  filter(State == "NE", County == "Kearney", Field == "104")
#hh <- sample(fields34$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields35 <- selection2 %>%
  filter(State == "NE", County == "Kearney", Field == "10")
ii <- sample(fields35$Collection_ID, size = 3, replace = FALSE)

fields36 <- selection2 %>%
  filter(State == "NE", County == "Cuming", Field == "66")
#jj <- sample(fields36$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields37 <- selection2 %>%
  filter(State == "NE", County == "Pierce", Field == "97")
#kk- sample(fields37$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields38 <- selection2 %>%
  filter(State == "NE", County == "Knox", Field == "99")
ll <- sample(fields38$Collection_ID, size = 3, replace = FALSE)

fields39 <- selection2 %>%
  filter(State == "IA", County == "Howard", Field == "howard")
# mm <- sample(fields39$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields40 <- selection2 %>%
  filter(State == "IA", County == "Chickasaw", Field == "chi")
# nn <- sample(fields40$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields41 <- selection2 %>%
  filter(State == "IA", County == "Floyd", Field == "floyd")
# oo <- sample(fields41$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields42 <- selection2 %>%
  filter(State == "IA", County == "Story", Field == "sto")
pp <- sample(fields42$Collection_ID, size = 3, replace = FALSE)

fields43 <- selection2 %>%
  filter(State == "IA", County == "Shelby", Field == "sh")
qq <- sample(fields43$Collection_ID, size = 3, replace = FALSE)

fields44 <- selection2 %>%
  filter(State == "IA", County == "Benton", Field == "be")
rr <- sample(fields44$Collection_ID, size = 3, replace = FALSE)

fields45 <- selection2 %>%
  filter(State == "IA", County == "Tama", Field == "ta")
ss <- sample(fields45$Collection_ID, size = 3, replace = FALSE)

fields46 <- selection2 %>%
  filter(State == "WI", County == "Sauk City", Field == "sa")
tt <- sample(fields46$Collection_ID, size = 3, replace = FALSE)

fields47 <- selection2 %>%
  filter(State == "WI", County == "Cuba City", Field == "cu")
uu <- sample(fields47$Collection_ID, size = 3, replace = FALSE)

fields48 <- selection2 %>%
  filter(State == "WI", County == "Waushara", Field == "wau")
vv <- sample(fields48$Collection_ID, size = 3, replace = FALSE)

fields49 <- selection2 %>%
  filter(State == "WI", County == "Grant", Field == "la")
ww <- sample(fields49$Collection_ID, size = 3, replace = FALSE)

fields50 <- selection2 %>%
  filter(State == "WI", County == "Iowa", Field == "co")
# xx <- sample(fields50$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields51 <- selection2 %>%
  filter(State == "WI", County == "Rock", Field == "cern")
# yy <- sample(fields51$Collection_ID, size = 3, replace = FALSE) less than 3 isolates per field

fields52 <- selection2 %>%
  filter(State == "WI", County == "Rock", Field == "cer")
zz <- sample(fields52$Collection_ID, size = 3, replace = FALSE)

fields53 <- selection2 %>%
  filter(State == "MI", County == "Allegan", Field == "Al")
aaa <- sample(fields53$Collection_ID, size = 3, replace = FALSE)

```
Once all filters, add a new column called "selected" to the master mix dataframe 
```{r}
selection <- selection %>%
  mutate(
    Selected = case_when(
      Collection_ID %in% selection1$Collection_ID ~ "selected",# filtering and naming "selected"" in case of in
      Collection_ID %in% a ~ "selected",
      Collection_ID %in% b ~ "selected",
      Collection_ID %in% c ~ "selected",
      Collection_ID %in% d ~ "selected",
      Collection_ID %in% e ~ "selected",
      Collection_ID %in% f ~ "selected",
      Collection_ID %in% g ~ "selected",
      Collection_ID %in% h ~ "selected",
      Collection_ID %in% i ~ "selected",
      Collection_ID %in% l ~ "selected",
      Collection_ID %in% m ~ "selected",
      Collection_ID %in% n ~ "selected",
      Collection_ID %in% o ~ "selected",
      Collection_ID %in% p ~ "selected",
      Collection_ID %in% q ~ "selected",
      Collection_ID %in% r ~ "selected",
      Collection_ID %in% s ~ "selected",
      Collection_ID %in% u ~ "selected",
      Collection_ID %in% v ~ "selected",
      Collection_ID %in% ww ~ "selected",
      Collection_ID %in% x ~ "selected",
      Collection_ID %in% y ~ "selected",
      Collection_ID %in% z ~ "selected",
      Collection_ID %in% aa ~ "selected",
      Collection_ID %in% bb ~ "selected",
      Collection_ID %in% cc ~ "selected",
      Collection_ID %in% dd ~ "selected",
      Collection_ID %in% ee ~ "selected",
      Collection_ID %in% ff ~ "selected",
      Collection_ID %in% gg ~ "selected",
      Collection_ID %in% ii ~ "selected",
      Collection_ID %in% ll ~ "selected",
      Collection_ID %in% pp ~ "selected",
      Collection_ID %in% rr ~ "selected",
      Collection_ID %in% ss ~ "selected",
      Collection_ID %in% tt ~ "selected",
      Collection_ID %in% uu ~ "selected",
      Collection_ID %in% vv ~ "selected",
      Collection_ID %in% ww ~ "selected",
      Collection_ID %in% zz ~ "selected",
      Collection_ID %in% aaa ~ "selected",
      TRUE ~ "not_selected"# in case of not, naming "not_selected""
    )
  )  

```
General Visualization of the US midewest isolates
```{r, echo=FALSE}
base <-
  mid_west_base + geom_point(# using basis of the previous subdata
    data = wm1_,
    aes(x = long, y = lat, color = Origin),
    inherit.aes = FALSE,
    size = 1,
    na.rm = TRUE,
    shape = 22,
    stroke = 0.5,
    fill = "white"
  ) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean inventory from Midwest") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
base

#Subdata by "Farmer fields""
WMfarmerfields <- wm1_ %>%
  group_by(State, Year, Origin) %>%
  filter(Origin == "Farmer fields")

base2 <-
  mid_west_base + geom_point(# using basis of the previous subdata
    data = WMfarmerfields,
    aes(x = long, y = lat, color = Year),
    inherit.aes = FALSE,
    size = 1,
    na.rm = TRUE,
    shape = 22,
    stroke = 0.5,
    fill = "white"
  ) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum of Farmer Field Soybean from Midwest") + theme(plot.title = element_text(  size = 10,
  face = "bold",
  hjust = 0.5,
  family = "Helvetica"
))
base2

#Subdata by Fungicide field trials
WMfungicide <- wm1_ %>%
  group_by(State, Year, Origin) %>%
  filter(Origin == "Fungicide field trials")

base3 <-
  mid_west_base + geom_point(# using basis of the previous subdata
    data = WMfungicide,
    aes(x = long, y = lat, color = Year),
    inherit.aes = FALSE,
    size = 1,
    na.rm = TRUE,
    shape = 22,
    stroke = 0.5,
    fill = "white"
  ) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum of Fungicide Field Trials Soybean from Midwest") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
base3
```
Selection of the State of Nebraska  
As we can noticed prevously for this state, there are no fungicide field trials, in other words, there are just farmer fields
```{r, echo=FALSE}
WM1S <- selection %>%# creating a subdata of NE
  group_by(State, Origin) %>%
  filter(Origin == "Farmer fields", State == "NE") %>%
  ungroup()

WM1S$DNA.Extraction = factor(WM1S$DNA.Extraction ,
                             levels = c("No DNA extraction", "Yes DNA extraction"))#Ordering the levels of DNA.Extraction
NE_county <- subset(counties, region == "nebraska")# Subsetting just for NE state

NE_county_base <-# Creating the base to use for next plots
  ggplot(data = NE_county,
         mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "grey")

#Plot of NE selection
face <- NE_county_base + geom_point(
  data = WM1S,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) + #Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean selection from Nebraska") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
face

# As we can noticed for DNA extraction here, it's been used those furthest places

# Now closer sight by counties
NE_counties <-
  counties %>% group_by(region) %>% filter(region == "nebraska") %>% ungroup %>% filter(#filterring by those counties with more fields
    subregion == "antelope" |
      subregion == "madison" |
      subregion == "cedar" |
      subregion == "cuming" |
      subregion == "dodge" |
      subregion == "boone" |
      subregion == "holt" |
      subregion == "valley" |
      subregion == "greeley" |
      subregion == "sherman" |
      subregion == "howard"
  )

# new object created in order to get the center of the polygon and place there the name of each county
centroid <-
  aggregate(data = NE_counties, cbind(long, lat) ~ subregion, FUN = mean)# getting the average

#Plotting the polygon using the as basis the centroid object created previously
NE_counties_base <-  ggplot(data = NE_counties,
                            mapping = aes(x = long, y = lat, group = subregion)) +# here the group means the counties
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "grey") +  geom_text(
    data = centroid,
    aes(label = subregion, x = long, y = lat),
    check_overlap = TRUE,
    size = 3
  )
#Plot of NE selection with counties delimitation
hand <- NE_counties_base + geom_point(
  data = WM1S,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) + #Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean selection from Nebraska") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
hand

```
Selection of the State of Iowa  
```{r, echo=FALSE}
WM_IA <- selection %>%# creating a subdata of IA
  filter(State == "IA")

WM_IA$DNA.Extraction = factor(WM_IA$DNA.Extraction ,
                             levels = c("No DNA extraction", "Yes DNA extraction"))#Ordering the levels of DNA.Extraction


WM_IA$Status = factor(WM_IA$Fungicide_status , levels = c("tested", "no_tested"))#Ordering the levels of Fungicide pre-tested

NE_county_base <-# Subsetting just for NE state
IA_county <- subset(counties, region == "iowa")# Creating the base to use for next plots
IA_county_base <-
  ggplot(data = IA_county,
         mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "white")

#Plot of IA selection
eye <- IA_county_base  + geom_point(
  data = WM_IA,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) +#Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean inventory from Iowa") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
eye


# As we can noticed for DNA extraction here, it's been used those furthest places
# Now closer sight by counties

IA_counties <-
  counties %>% group_by(region) %>% filter(region == "iowa") %>% ungroup %>% filter(#filtering by those counties with more fields
    subregion == "floyd" |
      subregion == "butler" |
      subregion == "chickasaw" |
      subregion == "shelby" |
      subregion == "boone" |
      subregion == "polk" |
      subregion == "bremer" | subregion == "benton" | subregion == "tama"
  )
# new object created in order to get the center of the polygon and place there the name of each county
centroid_iowa <-
  aggregate(data = IA_counties, cbind(long, lat) ~ subregion, FUN = mean)

#Plotting the polygon using the as basis the centroid object created previously
IA_counties_base <-  ggplot(data = IA_counties,
                            mapping = aes(x = long, y = lat, group = subregion)) +# here the group means the counties
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "grey") +  geom_text(
    data = centroid_iowa,
    aes(label = subregion, x = long, y = lat),
    check_overlap = TRUE,
    size = 3
  )

#Plot of IA selection with counties delimitation
pinky <- IA_counties_base + geom_point(
  data = WM_IA,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) +#Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean inventory from Nebraska 'No fungicide tested'") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
pinky

```
Selection of the State of Wisconsin  
```{r, echo=FALSE}
WM_WI <- selection %>%# creating a subdata of WI
  filter(State == "WI")
#Ordering the levels of DNA.Extraction
WM_IA$DNA.Extraction = factor(WM_IA$DNA.Extraction ,
                             levels = c("No DNA extraction", "Yes DNA extraction"))

WM_WI$Status = factor(WM_WI$Fungicide_status , levels = c("tested", "no_tested"))#Ordering the levels of Fungicide pre-tested

# Subsetting just for WI state
WM_WIcounty <- subset(counties, region == "wisconsin")
WI_county_base <-# Creating the base to use for next plots
  ggplot(data = WM_WIcounty,
         mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "white")
#Plot of WI selection
nose <- WI_county_base  + geom_point(
  data = WM_WI,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) +#Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean selection from Iowa") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
nose

# As we can noticed for DNA extraction here, it's been used those furthest places
# Now closer sight by countiesWI_counties <-

WI_counties <-
  counties %>% group_by(region) %>% filter(region == "wisconsin") %>% ungroup %>% filter(#filtering by those counties with more fields
    subregion == "walworth" |
      subregion == "grant" |
      subregion == "lafayette" |
      subregion == "waushara" | subregion == "adams" | subregion == "dane"
  )
 
  # new object created in order to get the center of the polygon and place there the name of each county
centroid_wisconsin <-
  aggregate(data = WI_counties, cbind(long, lat) ~ subregion, FUN = mean)

#Plotting the polygon using the as basis the centroid object created previously
WI_counties_base <-  ggplot(data = WI_counties,
                            mapping = aes(x = long, y = lat, group = subregion)) +# here the group means the counties
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "grey") +  geom_text(
    data = centroid_wisconsin,
    aes(label = subregion, x = long, y = lat),
    check_overlap = TRUE,
    size = 3
  )
#Plot of WI selection with counties delimitation
pointfinger <- WI_counties_base + geom_point(
  data = WM_WI,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) +#Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean inventory from Nebraska 'No fungicide tested'") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
pointfinger

```

```{r, echo=FALSE}
#Michigan#
WM_MI <- selection %>%# creating a subdata of MI
  filter(State == "MI")
#Ordering the levels of DNA.Extraction
WM_MI$DNA.Extraction = factor(WM_MI$DNA.Extraction ,
                             levels = c("No DNA extraction", "Yes DNA extraction"))#Ordering the levels of DNA.Extraction

WM_MI$Status = factor(WM_MI$Fungicide_status , levels = c("tested", "no_tested"))#Ordering the levels of Fungicide pre-tested

# Subsetting just for MI state
WM_MIcounty <- subset(counties, region == "michigan")
WM_county_base <-# Creating the base to use for next plots
  ggplot(data = WM_MIcounty,
         mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "white")

#Plot of NE selection
mouth <- WM_county_base  + geom_point(
  data = WM_MI,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) +#Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean inventory from Iowa") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
mouth

# As we can noticed for DNA extraction here, it's been used those furthest places
# Now closer sight by counties

MI_counties <-
  counties %>% group_by(region) %>% filter(region == "michigan") %>% ungroup %>% filter(#filtering by those counties with more fields
    subregion == "montcalm" |
      subregion == "ingham" |
      subregion == "allegan" |
      subregion == "ionia" |
      subregion == "joseph" | subregion == "hillsdale" |
      subregion == "sanilac"
  )
# new object created in order to get the center of the polygon and place there the name of each county
centroid_michigan <-
  aggregate(data = MI_counties, cbind(long, lat) ~ subregion, FUN = mean)

#Plotting the polygon using the as basis the centroid object created previously
MI_counties_base <-  ggplot(data = MI_counties,
                            mapping = aes(x = long, y = lat, group = subregion)) +# here the group means the counties
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "grey") +  geom_text(
    data = centroid_michigan,
    aes(label = subregion, x = long, y = lat),
    check_overlap = TRUE,
    size = 3
  )
#Plot of MI selection with counties delimitation
anularfinger <- MI_counties_base  + geom_point(
  data = WM_MI,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year,# by shape the level of Year
    size = DNA.Extraction# by size the level of DNA.Extraction
  ),
  inherit.aes = FALSE,
  na.rm = TRUE
) + theme(legend.position = "bottom") + facet_wrap( ~ num_isolates_per_field) + #Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Soybean inventory from Nebraska 'No fungicide tested'") + theme(plot.title = element_text(
    size = 10,
    face = "bold",
    hjust = 0.5,
    family = "Helvetica"
  ))
anularfinger

```
Selection of the country of Mexico  
```{r}
# Creating the base map for subsequent plots
mexico_base <-
  ggplot(data = mexico,
         mapping = aes(x = long, y = lat, group = group)) +
  coord_fixed(1.3) +
  geom_polygon(color = "black", fill = "grey")

wm2_ <-  wm1 %>%
  mutate(Fungicide_status = ifelse(Collection_ID  %in% tested,# Creating a new column based wheater or not fungicides pretested
                                   "tested", "no_tested")) %>%# Creating a new column based wheater or not fungicides pretested
  group_by(Field) %>% mutate (num_isolates_per_field = ifelse(n() > 2, "2>isolates/Field", "<2isolates/Field")) %>%#Creating a new column if the number of isolates/field is major than 2 "<2isolates/Field"
  ungroup() %>%
  filter(Collection_ID  %in% mexican_isolates) #Filtering mexican isolates


wm2_$num_isolates_per_field <-#Converting  as factor the levels of the new columns
  as.factor(wm2_$num_isolates_per_field)




```
Cleaning and making some arrangemments from the inventory so far, run twice
```{r}
wm2_$long <- as.numeric(as.character(wm2_$long))# Transforming long variables to numeric
wm2_$long <- (wm2_$long) * -1 # Transforming the long variable to the Hemispher West side



```
Data wrangling
```{r, echo=FALSE}
# creating a subdata of selection_Mexico
selection_Mexico <-
  wm2_ %>% select(
    Collection_ID,
    State,
    County,
    Field,
    Year,
    Origin,
    long,
    lat,
    hyphal_tip..ht.,
    DNA.Extraction,
    Serial_agar_dilution_for_creating_the_model_..N.20.,
    Form.ID,
    Fungicide_status,
    num_isolates_per_field
  ) %>%# Selecting 15 the most important columns so far
  group_by(State, County, Field) %>%
  mutate(num_ISO_per_field = n()) %>%
  ungroup %>%
  group_by(County) %>%
  mutate(num_field_County = length(unique(factor(Field)))) %>%
  select(
    Collection_ID,
    State,
    County,
    Field,
    num_ISO_per_field,
    num_field_County,
    Year,
    Origin,
    long,
    lat,
    hyphal_tip..ht.,
    DNA.Extraction,
    Serial_agar_dilution_for_creating_the_model_..N.20.,
    Form.ID,
    Fungicide_status,
    num_isolates_per_field
  )
#Subdata for randomly selection of those 3 isolates/field/county/state
selection_Mexico1 <- selection_Mexico %>%
  ungroup() %>%
  group_by(State, County, Field) %>%#grouping in order to select 3 isolates/field/County/State
  filter(num_ISO_per_field > 10,
         Fungicide_status == "no_tested") %>%# Filtering those fields with more than 10 isolates/ field and also by no fungicide pre-tested. Here the original idea was to filter by 3 >= isolates but  it does not not work with the next pipe available from tidyverse
  sample_n(3, replace = F)#Randomly sampled 3 isolates from the 10 available from each group

# Subdata another one to work with those groups with less than 10 isolates and more or equal to 3 isolates. The way to do it was to rest to the ones done
selection_Mexico2 <- selection_Mexico %>% # using the dataframe Selection_Mexico 
  ungroup() %>%
  group_by(State, County, Field) %>%#grouping in order to select 3 isolates/field/County/State
  filter(!num_ISO_per_field %in% selection_Mexico1$num_ISO_per_field) %>%
  filter(Fungicide_status == "no_tested") %>% #filtering those already done and also by no fungicide pre-tested
  ungroup()
```
Finding randomly either by function or by hand writing  3 samples for each (by sample function) field for those groupings with less than 10 isolates/field. In those cases of error it is due there is less than 3 isolates per field but it still being okay
```{r, echo=FALSE}
bbb <-
  sample(selection_Mexico2$Collection_ID,# sampling 3 for each group
         size = 3,
         replace = FALSE)


```
Once all filters, add a new column called "selected" to the master mix dataframe
```{r, echo=FALSE}
selection_Mexico <- selection_Mexico %>%
  mutate(
    Selected = case_when(
      Collection_ID %in% selection_Mexico1$Collection_ID ~ "selected",# filtering and naming "selected"" in case of in
      Collection_ID %in% bbb ~ "selected",
      TRUE ~ "not_selected"# in case of not, naming "not_selected""
    )
  )
#Plot of Mexico selection
eyebrow <- mexico_base + geom_point(
  data = selection_Mexico,
  aes(
    x = long,
    y = lat,
    color = Selected,# by color the level of selection
    shape = Year# by shape the level of Year
  ),
  inherit.aes = FALSE,
  na.rm = TRUE,
  size = 2
) + theme(legend.position = "bottom") + facet_wrap(~ Fungicide_status) + #Wrapping by the # of isolates/field
  scale_color_manual(values = c("red", "blue")) + theme(legend.position = "bottom") + labs(title = "Sclerotinia sclerotiorum Greenbean inventory from Mexico") + theme(plot.title = element_text(
  size = 10,
  face = "bold",
  hjust = 0.5,
  family = "Helvetica"
))
eyebrow

```

